Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
indent fix
By a small abuse of slight notation....

  \begin{definition}
  The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
  \end{definition}

@@

The first periodic DIT happen...

>>>>

  In an asynchronous system, the first DIT could happen before the arrival of at least one job of each task. We thus introduce the following notion:

  \begin{definition}
  The \textbf{first periodic DIT} of a system is the earliest DIT occurring strictly after the arrival of at least one job of each task.
  \end{definition}

  By a slight abuse of notation, it will also be noted $t_d$. Note that in the synchronous case the first periodic DIT is also the first DIT.

@@

The first periodic DIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in a stationary period, another DIT should have occurred in the transitive period (a contradiction).\\
